\documentclass[12pt, a4paper]{article}

% ==========================================
% LANGUAGE & FONT
% ==========================================
\usepackage{fontspec}
\setmainfont{Times New Roman}
\usepackage[english]{babel}
\usepackage{csquotes}           % Required by biblatex with babel

% ==========================================
% PAGE LAYOUT
% Left 3cm, Right 2cm, Top 2cm, Bottom 2cm
% ==========================================
\usepackage[top=2cm, bottom=2cm, left=3cm, right=2cm, headheight=15pt]{geometry}

% ==========================================
% HEADER & FOOTER
% ==========================================
\usepackage{fancyhdr}
\pagestyle{fancy}
\fancyhf{} % Clear default header and footer
\fancyhead[C]{\thepage} % Set page number at top center
\fancyfoot[C]{\footnotesize ©2026 Alpha Data Academy Co., Ltd. All rights reserved. Confidential and Proprietary.}
\renewcommand{\headrulewidth}{0pt} % Remove header line

% Redefine plain style so that title pages also have the same header and footer
\fancypagestyle{plain}{
  \fancyhf{}
  \fancyhead[C]{\thepage}
  \fancyfoot[C]{\footnotesize ©2026 Alpha Data Academy Co., Ltd. All rights reserved. Confidential and Proprietary.}
  \renewcommand{\headrulewidth}{0pt}
}

% ==========================================
% LINE SPACING
% ==========================================
\usepackage{setspace}
\onehalfspacing

% ==========================================
% FIGURES & TABLES
% ==========================================
\usepackage{graphicx}
\usepackage{booktabs}
\usepackage{multirow}
\usepackage{caption}
\usepackage{subcaption}
\usepackage{float}
\usepackage{tabularx}

% ==========================================
% MATH
% ==========================================
\usepackage{amsmath, amssymb}

% ==========================================
% PLOTS & COLORS
% ==========================================
\usepackage{pgfplots}
\pgfplotsset{compat=1.18}
\usepackage{xcolor}

% ==========================================
% TABLE OF CONTENTS STYLING
% ==========================================
\usepackage{tocloft}            % TOC formatting control
\usepackage{titlesec}           % Section title formatting

% TOC title style
\renewcommand{\cfttoctitlefont}{\large\bfseries}
\renewcommand{\cftaftertoctitle}{\\\rule{\linewidth}{0.4pt}}
\setlength{\cftbeforetoctitleskip}{0pt}
\setlength{\cftaftertoctitleskip}{12pt}

% Section entries in TOC — bold
\renewcommand{\cftsecfont}{\bfseries}
\renewcommand{\cftsecpagefont}{\bfseries}
\renewcommand{\cftsecleader}{\cftdotfill{\cftdotsep}}
\setlength{\cftsecindent}{0pt}
\setlength{\cftsecnumwidth}{2em}
\setlength{\cftbeforesecskip}{6pt}

% Subsection entries in TOC
\renewcommand{\cftsubsecfont}{\normalfont}
\renewcommand{\cftsubsecpagefont}{\normalfont}
\setlength{\cftsubsecindent}{2em}
\setlength{\cftsubsecnumwidth}{2.8em}
\setlength{\cftbeforesubsecskip}{2pt}

% Subsubsection entries in TOC
\setlength{\cftsubsubsecindent}{4.5em}
\setlength{\cftsubsubsecnumwidth}{3.5em}

% Section title formatting in document body
\titleformat{\section}
  {\normalfont\fontsize{13}{15}\bfseries}{\thesection}{1em}{}
\titleformat{\subsection}
  {\normalfont\fontsize{12}{14}\bfseries}{\thesubsection}{1em}{}
\titleformat{\subsubsection}
  {\normalfont\fontsize{12}{14}\itshape}{\thesubsubsection}{1em}{}

% ==========================================
% MISCELLANEOUS
% ==========================================
\usepackage{url}
\usepackage{microtype}          % Improved text justification
\usepackage{parskip}            % Space between paragraphs

% ==========================================
% REFERENCE MANAGEMENT (APA)
% Must be loaded before hyperref
% ==========================================
\usepackage[backend=biber, style=apa, sorting=nyt]{biblatex}
\addbibresource{references.bib}

% ==========================================
% HYPERREF — always load LAST
% ==========================================
\usepackage[
  colorlinks=true,
  linkcolor=black,
  citecolor=blue,
  urlcolor=blue,
  bookmarks=true,
  pdfusetitle
]{hyperref}

\usepackage{tikz}
\usetikzlibrary{shapes.geometric, arrows.meta, positioning, fit}
\usepackage{placeins}

% ==========================================
% RESEARCH PAPER INFORMATION
% ==========================================
\title{
  \textbf{Multimodal A.I: \\
  A Revolution for Enterprise Digital Transformation in Vietnam}
}

\author{
  Nguyễn Đại Quân\texorpdfstring{\textsuperscript{1}}{[1]},
  Nguyễn Phú Nam \texorpdfstring{\textsuperscript{2}}{[2]},
  Trương Hoàng Tùng \texorpdfstring{\textsuperscript{3}}{[3]}
  Nguyễn Dương Hiếu \texorpdfstring{\textsuperscript{4}}{[4]} \\[6pt]
  \small\textit{\texorpdfstring{\textsuperscript{1}}{[1]}Mathematical Economics, National Economics University} \\
}
\date{\today}

% ==========================================
% MAIN BODY
% ==========================================
\begin{document}

\maketitle

\newpage
\vspace*{\fill}
\begin{center}
\textbf{\Large Confidentiality Statement}
\end{center}
\vspace{1cm}
\noindent This research report and all underlying data, methodologies, and findings are the exclusive intellectual property of Alpha Data Academy Co., Ltd. This document is submitted solely for the purpose of evaluation by the authorized selection committee and designated reviewers of this competition. By accepting this report, the reviewer acknowledges that this material is bound by strict confidentiality.

\vspace{0.5cm}
\noindent No part of this research may be reproduced, cited, or shared with third parties---including academic peers or commercial entities---without the express written permission of Alpha Data Academy Co., Ltd. All rights, including patent and copyright protections for the proprietary AI frameworks described herein, are fully reserved.
\vspace*{\fill}
\newpage

% ==========================================
% ABSTRACT
% ==========================================
\begin{abstract}
\noindent
Digital transformation in enterprises has accelerated the adoption of Cognitive Robotic Process Automation (RPA) capable of processing unstructured and multimodal inputs such as documents, images, and speech.
In this research, we conducted a case study of our client’s e-commerce platform demonstrates that integrating Multimodal AI yields significant benefits, including a 95.61\% quality score in product search, a 99.76\% accuracy in model code lookup, and the absorption of up to 416 hours of human-equivalent labor. \\
However, deploying end-to-end Large Language Models (LLMs) in high-frequency enterprise workflows introduces significant challenges related to prediction accuracy, computational latency, and operational cost.
Specifically, using flagship models like Gemini 2.5 Pro for large-scale operations can cost approximately \$30.00 per 1,000 documents, creating a substantial financial barrier.
To address these limitations, this study proposes a modular two-stage framework for multimodal information extraction and entity resolution designed for domain-specific enterprise environments.
The architecture separates signal interpretation from semantic reasoning: in the first stage, specialized perception modules—including Optical Character Recognition (OCR) and Automatic Speech Recognition (ASR)—convert noisy multimodal inputs into textual representations.
In the second stage, a unified LLM performs zero-shot structured entity extraction from the transcribed content.
To resolve extracted entities against large enterprise catalogs, the system employs a hybrid retrieval mechanism that combines dense semantic representations (Sentence-BERT) with sparse lexical matching (BM25), integrated through Reciprocal Rank Fusion (RRF).
Experimental evaluation demonstrates that the proposed system achieves high performance with F1-scores of 0.91 for visual inputs and 0.85 for acoustic inputs.
The hybrid retrieval module maintains a Recall@5 of 0.93 on a catalog containing 50,000 SKUs.
Furthermore, the architecture achieves an estimated operational cost of \$13.50 per 1,000 documents—a 55\% reduction compared to end-to-end deployment—while reducing the total human-equivalent workload by 87.5\%. 
These results indicate that a decoupled modular approach provides an efficient and scalable solution for integrating noisy multimodal data into structured enterprise pipelines.

\medskip
\noindent\textbf{Keywords}: Multimodal Information Extraction, Robotic Process Automation, Large Language Models, Hybrid Retrieval, Entity Resolution, Enterprise Automation.

\medskip
\noindent\textbf{JEL Classification:} O33, L86, M15
\end{abstract}

\newpage

% ==========================================
% TABLE OF CONTENTS (clickable via hyperref)
% ==========================================
{
  \hypersetup{linkcolor=black}   % TOC links in black (professional look)
  \setcounter{tocdepth}{3}       % Show: section / subsection / subsubsection
  \tableofcontents
}

\newpage

% ==========================================
% SECTION FILES
% ==========================================

\input{sections/1_introduction}
\input{sections/2_literature_review}
\input{sections/case_study}
\input{sections/3_methodology}
\input{sections/4_experimental_setup}
\input{sections/5_results} 
\input{sections/6_conclusion}

% ==========================================
% REFERENCES
% ==========================================
\newpage
\nocite{*}
\printbibliography[heading=bibintoc, title={References}]

\end{document}