\section{Introduction}

\subsection{Research Background}
Digital Transformation (DX) in Vietnam has evolved from an incipient strategic imperative into a foundational requirement for enterprise survival. In the current era, the focus of DX has matured beyond the initial "digitization" phase—the mere conversion of analog records into digital formats—and has reached the next critical stage: \textbf{Robotic Process Automation (RPA)}. Under the "National Digital Transformation Program to 2025, with a vision to 2030" (Decision No. 749/QD-TTg), RPA has emerged as a principal mechanism for this shift, acting as a "virtual employee" that interfaces between legacy IT systems and back-office processes to execute high-volume, repetitive tasks with superior speed and accuracy.

The landscape of automation is further revolutionized by the recent "explosion" of \textbf{Multimodal AI}. In 2025 and 2026, Multimodal AI has matured from a research curiosity into an industry necessity. By integrating text, images, audio, and video, these systems can capture context and relationships that were previously invisible to text-only models. This technology has delivered transformative impacts across various fields:
\begin{itemize}
    \item \textbf{Healthcare:} Enhancing diagnostic precision by fusing medical imaging with genomic and clinical data.
    \item \textbf{Manufacturing \& Automotive:} Predicting equipment failures by analyzing combined streams of sensor data, audio vibrations, and maintenance logs.
    \item \textbf{Retail \& E-commerce:} Redefining customer experiences through visual search and brand identification within social media video content.
    \item \textbf{Social Listening:} Automatically detecting brand logos and sentiment in cross-platform video and audio streams.
\end{itemize}

\subsection{Problem Statement: The Plateau of Rule-Based RPA}
While RPA has successfully automated structured functions like payroll and simple data entry, traditional rule-based RPA is reaching a significant plateau. Its rigid nature restricts it to processing highly structured data, whereas real-world B2B procurement in Vietnam is dominated by unstructured inputs: distorted handwritten invoices, various formats of delivery notes, and informal voice-based orders with regional linguistic nuances.

The theoretical power of Multimodal AI, as discussed in Section 1.1, offers a potential solution to these limitations by providing "sensory perception" to RPA workflows. However, deploying premier end-to-end multimodal models (such as GPT-5o or Gemini 2.5 Pro) directly for large-scale enterprise operations is prohibitively expensive.

For a typical B2B order processing task requiring $\sim$1,200 input tokens and 150 output tokens, using a model like Gemini 2.5 Pro can cost approximately \$30.00 per 1,000 documents. For a medium-sized enterprise processing 50,000 transactions per month, this translates to an unsustainable monthly API cost of \$1,500. Furthermore, sending raw multimodal data (audio/image) directly to end-to-end APIs significantly increases token consumption and latency. This financial and operational barrier necessitates a more optimized, modular architecture that maintains high accuracy while minimizing dependency on expensive flagship models.

\subsection{Case Context: Experimental Development}
To investigate a viable path toward cost-effective intelligent automation, this research presents and evaluates an experimental Multimodal-AI-integrated Ordering System developed by our research group for a client company (from now on referred as "the enterprise"). The system was designed to bridge the gap between the company's complex product catalog and the unstructured nature of field-based procurement. By decoupling signal interpretation from semantic reasoning, our research group aims to demonstrate a scalable, "production-ready" framework that can handle highly illegible handwriting, diverse printed document formats, multi-regional Vietnamese dialects, and the inconsistent product naming habits found in local trading while achieving an operational cost of only \$13.50 per 1,000 processed documents, significantly undercutting the cost of pure end-to-end flagship model deployment.

\subsection{Research Questions}
To investigate the practical implementation and value of these advanced technologies, this study poses two primary research questions:
\begin{enumerate}
    \item[\textbf{RQ1}] (\textit{Multimodal Applications}): In what ways can Multimodal AI be strategically applied to optimize enterprise workflows in the Vietnamese context?
    \item[\textbf{RQ2}] (\textit{Economic Efficiency}): To what extent does the deployment of a Multimodal-AI-integrated Ordering System improve operational economics—specifically regarding processing latency, human-equivalent labor reduction, and transaction costs—within a legacy manufacturing environment?
\end{enumerate}

\subsection{Research Contributions}
This study explores how Multimodal AI serves as a catalyst for Enterprise Digital Transformation in Vietnam through the following contributions:
\begin{itemize}
    \item \textbf{Case Study of Multimodal AI at the enterprise:} We document the practical application of Multimodal AI within a major legacy enterprise, highlighting its impact on Agentic Sales Advisory-a conversational system that autonomously reasons over customer queries to provide technical specifications, product discovery, and journey-based recommendations.
    \item \textbf{Framework for Multimodal AI in Enterprise DX:} We propose a modular, two-stage architecture that decouples signal interpretation from semantic reasoning. This allows perceptual tasks (OCR/ASR) to be handled by specialized modules while delegating higher-level reasoning to a Large Language Model (LLM), providing a scalable blueprint for noisy enterprise data pipelines.
    \item \textbf{Technical R\&D of the Multimodal-AI-integrated Ordering System:} We provide a technical evaluation of a system designed to achieve precise SKU mapping against an enterprise catalog of 50,000 items. The system utilizes a hybrid retrieval mechanism (BM25 + Vector Search) and Reciprocal Rank Fusion (RRF) to optimize accuracy and cost efficiency while limiting human intervention to 12.5\%.
\end{itemize}